Linear Variation and an Optimization of Algorithms for Connected Components Labeling in a Binary Image

### 2016-02-06 paper/paper.tex
Add 5000x7500 test
Max out tables width
Fix title capitalization
Add pictures instead of tables!

@@

\title{Linear variation and an optimization of algorithms for connected
components labeling in a binary image}

@@

@@

\newcommand{\inputtable}[2]{
  \begin{table}[p]
    \centering
    \input{../bench-out/#1x#2}
    \caption{Average milliseconds of cpu time per run on noise images $#1 \times #2$ px}
    \label{tab:noise#1x#2}
  \end{table} }

% \inputtable{200}{300}
% \inputtable{400}{600}
\inputtable{800}{1200}
% \inputtable{1200}{1800}
\inputtable{2000}{3000}
\inputtable{4000}{6000}

>>>>

\usepackage{tabularx}
\usepackage{graphicx}

@@

\title{Linear Variation and an Optimization of Algorithms for Connected
Components Labeling in a Binary Image}

@@

\newcommand{\inputtable}[2]{
  \begin{figure}
    \centering
    \includegraphics[height=0.45\textheight, keepaspectratio]{pics/#1x#2.eps}
    \caption{Average CPU time per run on noise images $#1 \times #2$ px}
    \label{fig:noise#1x#2}
  \end{figure}
  % \begin{table}[p]
    % \centering
    % \input{../bench-out/#1x#2}
    % \caption{Average milliseconds of cpu time per run on noise images $#1 \times #2$ px}
    % \label{tab:noise#1x#2}
  % \end{table}
}

% \inputtable{200}{300}
% \inputtable{400}{600}
\inputtable{800}{1200}
% \inputtable{1200}{1800}
\inputtable{2000}{3000}
\inputtable{4000}{6000}
\inputtable{5000}{7500}

@@
